The LSST-DESC 3x2pt Tomography Optimization Challenge

### 2021-08-23 paper/authors.tex
more affils
add another orcid
First half of comments from AIM looked at
add new figs
more text on overlap
author tweak and avoid repetition
add author statement and standard acks
CWR changes

\author[0000-0001-7363-7932]{Angus Wright}
\affiliation{Ruhr University Bochum, Faculty of Physics and Astronomy, Astronomical Institute (AIRUB), German Centre for Cosmological Lensing, 44780 Bochum, Germany}

@@

\author{Adam Broussard}
\noaffiliation

@@

\author{Eduardo S. Cypriano}
\affiliation{Universidade de S\~ao Paulo, IAG, Rua do Mat\~ao 1225, S\~ao Paulo, SP, Brazil}

\author{Bernardo M. O. Fraga}
\affiliation{Centro Brasileiro de Pesquisas F\'isicas, Rua Dr. Xavier Sigaud 150, 22290-180 Rio de Janeiro, RJ, Brazil}

@@

\author[0000-0002-0226-9893]{Elizabeth J. Gonzalez}
\affiliation{Instituto de Astronom\'{\i}a Te\'orica y Experimental (IATE-CONICET), Laprida 854, X5000BGR, C\'ordoba, Argentina.}

\affiliation{Observatorio Astron\'omico de C\'ordoba, Universidad Nacional de C\'ordoba, Laprida 854, X5000BGR, C\'ordoba, Argentina.}

@@

\author{Alex Malz}
\affiliation{Ruhr University Bochum, Faculty of Physics and Astronomy, Astronomical Institute (AIRUB), German Centre for Cosmological Lensing, 44780 Bochum, Germany}

\author{Andrina Nicola}
\noaffiliation

@@

\author{Andy Park}
\affiliation{Department of Physics and Astronomy, University of California, Irvine, CA 92697, USA}

\author{Anze Slosar}
\affiliation{Brookhaven National Laboratory, Upton NY 11973, USA}

\author{Gabriel Teixeira}
\affiliation{Centro Brasileiro de Pesquisas F\'isicas, Rua Dr. Xavier Sigaud 150, 22290-180 Rio de Janeiro, RJ, Brazil}

% DESC Builder authors
\author{Yao-Yuan Mao}
\noaffiliation

>>>>

\author[0000-0002-8676-1622]{Alex I. Malz}
\affiliation{German Centre of Cosmological Lensing, Ruhr-Universit\"{a}t, Universit\"{a}tsstra{\ss}e 150, 44801 Bochum, Germany}

\author[0000-0001-7363-7932]{Angus H. Wright}
\affiliation{Ruhr University Bochum, Faculty of Physics and Astronomy, Astronomical Institute (AIRUB), German Centre for Cosmological Lensing, 44780 Bochum, Germany}

\author[0000-0002-8713-3695]{An\v{z}e Slosar}
\affiliation{Brookhaven National Laboratory, Upton NY 11973, USA}

@@

\author[0000-0002-7767-5044]{Adam Broussard}
\affiliation{Department of Physics and Astronomy, Rutgers, the State University, Piscataway, NJ 08854, USA}

@@

\author[0000-0001-9196-7038]{Eduardo S. Cypriano}
\affiliation{Universidade de S\~ao Paulo, IAG, Rua do Mat\~ao 1225, S\~ao Paulo, SP, Brazil}

\author[0000-0002-6395-3410 ]{Bernardo M. O. Fraga}
\affiliation{Centro Brasileiro de Pesquisas F\'isicas, Rua Dr. Xavier Sigaud 150, 22290-180 Rio de Janeiro, RJ, Brazil}

@@

\author[0000-0002-0226-9893]{Elizabeth J. Gonzalez}
\affiliation{Centro Brasileiro de Pesquisas F\'isicas, Rua Dr. Xavier Sigaud 150, 22290-180 Rio de Janeiro, RJ, Brazil}
\affiliation{Instituto de Astronom\'{\i}a Te\'orica y Experimental (IATE-CONICET), Laprida 854, X5000BGR, C\'ordoba, Argentina.}
\affiliation{Observatorio Astron\'omico de C\'ordoba, Universidad Nacional de C\'ordoba, Laprida 854, X5000BGR, C\'ordoba, Argentina.}

@@

\author{Andrina Nicola}
\affiliation{Department of Astrophysical Sciences, Princeton University, Peyton Hall, Princeton, NJ 08544, USA}

@@

\author[0000-0002-8318-8226]{Andy Park}
\affiliation{Department of Physics and Astronomy, University of California, Irvine, CA 92697, USA}

\author[0000-0002-1594-208X]{Gabriel Teixeira}
\affiliation{Centro Brasileiro de Pesquisas F\'isicas, Rua Dr. Xavier Sigaud 150, 22290-180 Rio de Janeiro, RJ, Brazil}

\author[0000-0003-1468-8232]{Katrin Heitmann}
\affiliation{Argonne National Laboratory, 9700 S Cass Ave, Lemont, IL 60439, USA}

\author[0000-0002-2545-1989]{Eve Kovacs}
\affiliation{Argonne National Laboratory, 9700 S Cass Ave, Lemont, IL 60439, USA}

% DESC Builder authors
\author[0000-0002-1200-0820]{Yao-Yuan Mao}
\affiliation{Department of Physics and Astronomy, Rutgers University, Piscataway, NJ 08854, USA}
